Construction of Proto Digital Twin with ROS2 and Omniverse

### 2023-05-16 manuscripts/paper-1/Without_Names.tex
Revision

    \author{Alican Tüzün
    \and
    Georg Hackenberg
    }
    \institute{School of Engineering\\
    University of Applied Sciences Upper Austria\\
    4600 Wels, Upper Austria, Austria\\
    \email{alican.tuzuen@fh-wels.at}
    \email{georg.hackenberg@fh-wels.at}
    }

@@

    \begin{abstract}
        Digital twins are becoming more and more important for the efficient and effective development and operation of cyber-physical systems.
        However, digital twins are only useful if they reflect the real-world system accurately enough,
        i.e.\ their quality is high enough.
        This claim entails the question, of what the term quality in the context of digital twins means and
        how it can be measured. In this article, authors presented their experience with the quality assurance of a digital
        twin for an assembly line in the automotive industry.
        Authors explained the preliminary definition of digital twin quality, 
        which authors derived from classical quality models for general software systems.
        Furthermore, authors described quality issues, 
        which they were able to detect in a digital twin of an assembly line in the automotive industry.
        Finally, authors concluded how to leverage their experience in different contexts 
        and how to generalize the underlying approaches.
    \end{abstract}

@@

    \section{Method}
    The form of FELICE's digital twin was the digital twin instance, which implies that the real system was already constructed. It is important to note that, for the sake of convenience, the authors used the term "Digital Twin" in the subsequent chapters instead of  "digital twin instance" in the subsequent chapters.

@@

    \bibliography{main}
    \bibliographystyle{splncs04}

>>>>

@@

    \begin{abstract}
        Digital twins are becoming increasingly important for the efficient and effective development 
        and operation of cyber-physical systems.
        However, digital twins are only useful if they reflect the real-world system accurately enough,
        i.e.\ their quality is high enough.
        This claim entails the question, of what the term quality in the context of digital twins means and
        how it can be measured. In this article, the authors presented their experience with the quality assurance of a digital
        twin for an assembly line in the automotive industry.
        Authors explained the preliminary definition of digital twin quality, 
        which authors derived from classical quality models for general software systems.
        Furthermore, authors described quality issues, 
        which they were able to detect in a digital twin of an assembly line in the automotive industry.
        Finally, authors concluded how to leverage their experience in different contexts 
        and how to generalize the underlying approaches.
    \end{abstract}

@@

    \section{Method}
    The form of FELICE's digital twin was the digital twin instance\cite{GrievesVickers2017}, 
    which implies that the real system was already constructed. It is important to note that, for the sake of convenience, the authors used the term "Digital Twin" in the subsequent chapters instead of  "digital twin instance" in the subsequent chapters.

@@

    \newpage
    \bibliography{main}
    \bibliographystyle{splncs04}

### 2023-05-16 manuscripts/paper-2/main.tex
Revision

    \section{Introduction}\label{section:introduction}
    As new and complex technologies have advanced to emerge, it becomes progressively 
    difficult to understand and define their core concepts. One significant example in the 
    area of digitalization is the concept of digital twins, which has resulted in numerous definitions, that vary 
    from one derivation to another. Because, even though the terms `digital' and `twin' are easy to grasp,  their 
    consolidation develops a new challenging concept, which can be resulted in misunderstanding and misapplication. For example, 
    some authors claim that the first utilization of the digital twins 
    happened in Apollo 13 space mission in 1970. Even though there was a `twin' used to simulate the spacecraft in space, fulfilling the first part of the concept of 
    `digital twin', the digital component was missing, making this claim inaccurate.

>>>>

    \section{Introduction}\label{section:introduction}
    As new and complex technologies have advanced to emerge, it becomes progressively 
    difficult to understand and define their core concepts. One significant example in the 
    area of digitalization is the concept of digital twins, which has resulted in numerous definitions, that vary 
    from one derivation to another. Because, even though the terms `digital' and `twin' are easy to grasp,  their 
    consolidation emerge a new challenging concept, which can be resulted in misunderstanding and misapplication. For example, 
    some authors claim that the first utilization of the digital twins 
    happened in Apollo 13 space mission in 1970. Even though there was a `twin' used to simulate the spacecraft in space, fulfilling the first part of the concept of 
    `digital twin', the digital component was missing, making this claim inaccurate.
